Spatial Generalized Linear Models in \proglang{R} Using \pkg{spmodel}

### 2024-11-20 inst/manuscript/manuscript.qmd
some udpates

SPGLMs are fit in [spmodel]{.pkg} using a novel application of the Laplace approximation that marginalizes over the latent (i.e., unobserved) mean, $\mathbf{w}$, and the fixed effects, $\boldsymbol{\beta}$. The approach is quite flexible and accommodates any general response distribution and covariance structure.  @ver2024marginal show that the approach, as implemented in [spmodel]{.pkg}, generally yields unbiased estimators with proper interval coverage and often outperforms the Bayesian approach from [spBayes]{.pkg}, the INLA approach from [R-INLA]{.pkg}, and the automatic differentiation approach from [glmmTMB]{.fct}.

>>>>

SPGLMs are fit in [spmodel]{.pkg} using a novel application of the Laplace approximation that marginalizes over the latent (i.e., unobserved) mean, $\mathbf{w}$, and the fixed effects, $\boldsymbol{\beta}$. The approach is quite flexible and accommodates any general response distribution and covariance structure.  @ver2024marginal show that the approach, as implemented in [spmodel]{.pkg}, generally yields unbiased estimators with proper interval coverage and often outperforms the Bayesian approach from [spBayes]{.pkg}, the INLA approach from [R-INLA]{.pkg}, and the automatic differentiation approach from [glmmTMB]{.pkg}.

### 2024-11-20 inst/manuscript/manuscript.tex
some udpates

\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}{}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

SPGLMs are fit in \pkg{spmodel} using a novel application of the Laplace
approximation that marginalizes over the latent (i.e., unobserved) mean,
\(\mathbf{w}\), and the fixed effects, \(\boldsymbol{\beta}\). The
approach is quite flexible and accommodates any general response
distribution and covariance structure. \citet{ver2024marginal} show that
the approach, as implemented in \pkg{spmodel}, generally yields unbiased
estimators with proper interval coverage and often outperforms the
Bayesian approach from \pkg{spBayes}, the INLA approach from
\pkg{R-INLA}, and the automatic differentiation approach from
\fct{glmmTMB}.

@@

\renewcommand{\bibsection}{}
\bibliography{references.bib}

>>>>

\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}{}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, sharp corners, interior hidden]}{\end{tcolorbox}}\fi
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

SPGLMs are fit in \pkg{spmodel} using a novel application of the Laplace
approximation that marginalizes over the latent (i.e., unobserved) mean,
\(\mathbf{w}\), and the fixed effects, \(\boldsymbol{\beta}\). The
approach is quite flexible and accommodates any general response
distribution and covariance structure. \citet{ver2024marginal} show that
the approach, as implemented in \pkg{spmodel}, generally yields unbiased
estimators with proper interval coverage and often outperforms the
Bayesian approach from \pkg{spBayes}, the INLA approach from
\pkg{R-INLA}, and the automatic differentiation approach from
\pkg{glmmTMB}.

@@

%bib-loc-124C8010

  \bibliography{references.bib}
